Software variability in fMRI analysis:\\ comparing between-tool and numerical errors

### 2021-12-06 paper/paper.tex
Edited abstract

Numerical and software variability broadly affect structural, diffusion, and functional MRI analyses. Numerical
variability originates in software updates or code
parallelization, whereas software variability reflects discrepancies between
models implemented in different analysis software packages. While numerical
and software variability were both shown to impact analysis outcomes, the
extent to which these sources of variability compare for a given
analysis remains understudied. This work presents a comparison of
numerical and software variability for group-level and subject-level functional MRI analyses.
We reproduced a previous comparison between functional MRI analysis
software packages FSL, AFNI, and SPM, which we extended to measure
numerical variability through Monte-Carlo arithmetic.
Although We found that between-tool variability was larger than numerical variability,
we identified brain regions that numerical perturbations simulated between-tool variability.
Furthermore, we found more numerical instability in thresholded maps than unthresholded ones
and individual analysis than group-level analysis results. \tristan{Abstract to be fixed}

\end{abstract}

>>>>

Software variability broadly affects functional MRI analyses due to
differences among analytical tools and numerical instabilities. While
numerical and between-tool variability were both shown to impact analysis
outcomes, the extent to which these sources of variability compare for a
given analysis remains understudied. We extended a previous comparison
between fMRI analysis tools FSL, AFNI, and SPM, to measure numerical
variability through Monte-Carlo arithmetic. We found that in group analyses
between-tool variability was consistently larger than machine error,
whereas in subject analyses machine error approached between-tool
variability in some cases. Furthermore, between-tool variability and
machine error appeared moderately correlated in all tested conditions.
Finally, we found that numerical error at the precision of 17 bits --- a
precision level found in commonly-used libraries --- had effects of similar
magnitude \tristan{check that} than between-tool variability. Our findings motivate the
continued investigation of numerical instability in neuroimaging, and position it 
as a possible proxy for between-tool variations.
\end{abstract}
